Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-02-17 draft_p2.tex
Updates legend for illustr_extrms_vorticity, illustr_density_streamlines and timeseries_extremes

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{illustr_extrms_vorticity/illustr_extrms_vorticity.png}
  \caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for the four highest drag fluctuations in the timeseries. The corresponding drag timeseries can be found in figure~\ref{fig:extremes_timeseries}.
    The high value for the drag results from the formation of a strong negative (red) vortex inducing a pressure drop at the base of the obstacle. The formation of such a structure is aided by important vorticity production at the bottom boundary of the obstacle coupled with the influence of positive vorticity in the vicinity of the base.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.5\linewidth]{illustr_density_streamlines/illustr_density_streamlines.png}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.5\linewidth]{timeseries_extremes/timeseries_extremes.png}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{illustr_extrms_vorticity/illustr_extrms_vorticity.png}
  \caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for some of the highest drag fluctuations in the control timeseries.
    The extreme value for the drag results from the concentration of vorticity in the vicinity of the base of the obstacle, causing a pressure drop.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.5\linewidth]{illustr_density_streamlines/illustr_density_streamlines.png}
  \label{density+streamlines}
  \caption{Pressure field and velocity streamlines in the vicinity of the obstacle at $t=t^{\star}$. Becasue of the blocking vortex, vorticity produced along the top boundary of the obsatcle has no other choice but to accumulate at the base of the obstacle.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{timeseries_extremes/timeseries_extremes.png}
  \caption{Average drag timeseries in the vicinity of an extreme drag fluctuation at $t=t^{\star}$. The blue continuous line results from an average over the 104 extreme events sampled in the control run. This illustrates that extreme drag variations are very local in time, with a typical lifetime of one correlation time unit $\tau_c$.}
\end{figure}
